Millions of Type Errors

### 2023-09-13 programming23/paper.tex
note some outliner telemetry records

\begin{figure}[t]
  % ;; (list* (max* vv) (median < vv) mm (stddev/mean mm vv) (percentile* vv)))
  % ;; percentile* = 0.95 -- 0.99
  %#hash((editrange . (1156036 926 3007043/817 30975.40553032358 (0.95 8220) (0.96 9858) (0.97 13656) (0.98 18956) (0.99 34725)))
  %      (event-count . (6079 138 38689/135 582.5752201972966 (0.95 960) (0.96 1174) (0.97 1304) (0.98 1836) (0.99 3302)))
  %      (files . (54884 7678 55257996/4639 11853.650098459446 (0.95 40029) (0.96 42771) (0.97 45417) (0.98 48688) (0.99 51761)))
  %      (lines . (1089963 3115 38928947/5992 22364.75846303099 (0.95 18561) (0.96 25892) (0.97 27014) (0.98 29725) (0.99 50547)))
  %      (timespan . (1387897376 845648 591343604248/185705 15724745.722577972 (0.95 10696064) (0.96 12715468) (0.97 15596940) (0.98 21153924) (0.99 35450460))))

@@

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}{l@{}r@{~}l@{}r@{~}l} \\
                   & Time Span (sec)  &       & Record Count  \\
      Mean [std]   &     3,184 & \stddev{16}  &     286 & [583] \\
      Median       &       845 &              &     138        \\
      \pct{99}     &    35,450 &              &   3,302        \\
      & \includegraphics[width=0.2\columnwidth]{img/timespan-distribution.pdf}
      & & \includegraphics[width=0.2\columnwidth]{img/event-count-distribution.pdf}

@@

    15 days

@@

Fourteen errors never showed up.
Nothing for \code{CodeTooComplex} or \code{UnificationTooComplex} is great news.
But what about the others? FILL

@@

@@

To deal with pathologies such as the worst-case time for ML-style type
inference~\cite{m-popl-1990,ktu-caap-1990}, the typechecker
has two internal limits to restrict the problems it will attempt to solve.
Hitting a limit triggers either a \code{CodeTooComplex} or
\code{UnificationTooComplex} error.
A casual user should never see these errors.

@@

Thanks to Ben(jamin?) Chung for feedback on plots and data analysis advice.
Greenman was supported by
grant \href{https://nsf.gov/awardsearch/showAward?AWD_ID=2030859&HistoricalAwards=false}{2030859}
to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.

>>>>

\begin{figure}[t]
  % ;; (list* (max* vv) (median < vv) mm (stddev/mean mm vv) (percentile* vv)))
  % ;; percentile* = 0.95 -- 0.99
  %#hash((editrange . (1156036 926 3007043/817 30975.40553032358 (0.95 8220) (0.96 9858) (0.97 13656) (0.98 18956) (0.99 34725)))
  %      (event-count . (6079 138 38689/135 582.5752201972966 (0.95 960) (0.96 1174) (0.97 1304) (0.98 1836) (0.99 3302)))
  %      (files . (54884 7678 55257996/4639 11853.650098459446 (0.95 40029) (0.96 42771) (0.97 45417) (0.98 48688) (0.99 51761)))
  %      (lines . (1089963 3115 38928947/5992 22364.75846303099 (0.95 18561) (0.96 25892) (0.97 27014) (0.98 29725) (0.99 50547)))
  %      (timespan . (1387897376 845648 591343604248/185705 15724745.722577972 (0.95 10696064) (0.96 12715468) (0.97 15596940) (0.98 21153924) (0.99 35450460))))
  %% NOTE: 3 records have +1M lines, all from one nocheck session, all with 3 files
  %% - session "30,762,216,447,324"
  %% NOTE: 133 records have +52K files, all from one nocheck session
  %% - session "330,172,870,224,081" 
  %% (2nd biggest has 41K files "31,650,473,913,529")

@@

  \begin{subfigure}[t]{\columnwidth}
    %% NOTE max time = 1 million seconds = 15 days

    \begin{tabular}{l@{}r@{~}l@{}r@{~}l} \\
                   & Time Span (sec)  &       & Record Count  \\
      Mean [std]   &     3,184 & \stddev{16}  &     286 & [583] \\
      Median       &       845 &              &     138        \\
      \pct{99}     &    35,450 &              &   3,302        \\
      & \includegraphics[width=0.2\columnwidth]{img/timespan-distribution.pdf}
      & & \includegraphics[width=0.2\columnwidth]{img/event-count-distribution.pdf}

@@

@@

FILL N errors never showed up.
Nothing for \code{CodeTooComplex} or \code{UnificationTooComplex} is great news.
But what about the others? FILL

@@

\subsection{Internal Error}
%% out/te-editrange-*

FILL hope to never see \code{InternalError}.
Have zero, yay!

@@

To deal with pathologies such as the worst-case time for ML-style type
inference~\cite{m-popl-1990,ktu-caap-1990}, the typechecker
has internal limits that restrict the problems it will attempt to solve.
Hitting a limit triggers one of the following errors:
\code{CodeTooComplex},
\code{NormalizationTooComplex}, or
\code{UnificationTooComplex}.
A casual user should never see these errors.

@@

Thanks to Benjamin Chung for feedback on plots and data analysis advice.
Greenman was supported by
grant \href{https://nsf.gov/awardsearch/showAward?AWD_ID=2030859&HistoricalAwards=false}{2030859}
to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.
